\documentclass[a4paper,11pt]{article}
% -----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.70in, left=0.4in, right=0.93in]{geometry}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{wasysym}
\usepackage[misc]{ifsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}
\raggedbottom
\usepackage{tikz}

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.45cm}
\newcommand{\psep}{-0.6cm}

\pagestyle{empty}
% -----------------------------------------------------------
% Custom commands
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newcommand{\resitem}[1]{\item #1}

\newcommand{\resheading}[1]{
  \hspace{-6pt}
  \begin{minipage}{\textwidth+2pt}
    \textbf{\textsc{\large #1}}
    \vspace{4pt}
    \hrule
  \end{minipage}
}

\newcommand{\resSubHeading}[2]{
  \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{#1} & \textit{#2}\\
  \end{tabular*}
}

\newcommand{\taHeading}[2]{
  \begin{tabular*}{\textwidth}{ll @{\extracolsep{\fill}} r}
    \hspace{10pt} & \textbf{#1} & \textit{#2}\\
  \end{tabular*}
}

\newcommand{\resDeepSubHeading}[4]{
  \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{#1} & \textit{#2} \\
    \textit{#3} & \textit{#4}
  \end{tabular*}
}

\newcommand{\resEduHeading}[5]{
  \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{\large #1} \\
    \textit{#2} & \textit{#3} \\
    {\large #4} & \textit{CGPA: \textbf{#5}}
  \end{tabular*}
}

\newcommand{\resCompany}[1]{
    \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \large \textbf{#1}
  \end{tabular*}
}

\newcommand{\resPosition}[2]{
    \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
        \textit{#1} & \textit{#2}
    \end{tabular*}
}

\def\Plus{\texttt{+}}


% -----------------------------------------------------------
\begin{document}
\begin{center}
  {\Huge Saswata Dutta}\\
  \href{mailto:saswat.dutta@gmail.com}{\faEnvelope \texttt{ saswat.dutta@gmail.com}}\hspace{1em}
  \href{https://www.linkedin.com/in/saswata-dutta/}{\faLinkedinSquare \texttt{ saswata-dutta}}\hspace{1em}
  {\faPhone \texttt{ +91-8178349520}}\hspace{1em}
\end{center}

\vspace{-8pt}
\noindent\makebox[\linewidth]{\rule{\paperwidth+10em}{0.8pt}}\\

%%%%%%%%%%%%%%%%%%%

    \indent \resheading{Skills}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt]
        \setlength{\itemsep}{-3pt}
        \resitem {Large Scale Data Intensive Applications, Big Data, Database Scaling}
        \resitem {Machine Learning, Machine Learning Platform, MLOps}
        \resitem {NLP, Generative AI, LLM, RAG, LLMOps, Chatbots}
        \resitem {AWS, GCP, Azure}
        \resitem{Leading technical charter for teams with 30+ engineers.}
    \end{itemize}
    
%%%%%%%%%%%%%%%%%%%
    \indent \resheading{Experience}

    
    \indent \resCompany{Coinbase}
        \indent \resPosition{Staff Software Engineer}{Oct 2023 - Present}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \resitem{Built a \textbf{scalable, multi-cloud LLM platform} , enabling multiple high-volume use cases, optimized for token efficiency, and supporting large-scale semantic and full-text search across knowledge bases, resulting in \textbf{\$60M} in cost savings. The system elastically scaled and handled multiple bullruns, with peak consumption of \textbf{100M} tokens per minute}

            \resitem{Leveraged LLMs to enhance customer support; achieved a \textbf{65\%} automated resolutions, expanded coverage to \textbf{18} new countries. Optimized costs to only \textbf{\$2K} per month through semantic caching, enabling the solution to gracefully handle traffic spikes of up to \textbf{10x}.}
            
            \resitem{Developed cheap, customizable and compliance focussed guardrails, evaluation frameworks, and audit trail for critical business processes in Finance and Legal operations.}  
        
            \resitem{Led various LLM-powered initiatives to enhance employee productivity, including coding assistants, on-call operations, Slack helpers, and various Legal and Finance business process automations.}

            \resitem{Leveraging LLM-as-a-Judge for automated and scalable evaluations and auto tuning prompts.}

            \resitem{Developed plugins for seamless integration of in-house LLM endpoints across popular agent frameworks (LangGraph, LangFlow, CrewAI, Legion AI, Bedrock Agents), enhancing developer workflow.}
        
            \resitem{\textbf{Technologies:} \textit{LLMs: AWS Bedrock, GCP Vertex AI, Azure OpenAI, Anthropic, Huggingface, RAG, CAG, LangChain, LangGraph, DeepEval, VectorStore, MongoDB, AWS Aurora, Opensearch.}}
            
        \end{itemize}

%%%%%%%%%%%%%%%%%%%

    \indent \resCompany{Amazon}
        \indent \resPosition{Staff Software Engineer}{Mar 2020 - Oct 2023}
        \indent \textit{AWS EMR}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            
            \resitem{Optimized AWS EMR Spark performance via improved query planning, S3 interactions, and JVM memory optimizations, achieving significant performance gains in TPC-DS.}
            
            \resitem{Enhanced performance via prefetch and dynamic partition pruning, optimal join strategies.}

            \resitem{\textbf{Technologies:} \textit{AWS EMR, Apache Spark, Trino, S3, DynamoDb, JVM}}
            
        \end{itemize}

        \indent \textit{Amazon Business Automation}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            
            \resitem{Modernized Amazon's fraud and anomaly detection framework at a global scale by integrating real-time streaming to GNNs, reducing detection/mitigation times from weeks to one day.}
            
            \resitem{Architected a global scale serverless Data Lake for interactive analytics and machine learning training, resulting in a 3x improvement in operational metrics and a 10x reduction in costs.}
            
            \resitem{Built large-scale knowledge graphs with \textbf{50B} vertices to power GNN models. Efficiently caching subgraphs to reduce feature store costs by \textbf{\$500k annually}.}

            \resitem{Revamped the account management ecosystem by optimizing billing and metering pipelines, reducing turnaround time by \textbf{70\%}. Enhanced rule engines to improve performance and cut costs by \textbf{65\%}.}

            \resitem{\textbf{Technologies:} \textit{AWS (Neptune, Textract, Comprehend, RDS Postgres, EMR, Athena, Lambda, SQS, SNS, DynamoDB, Redshift, OpenSearch, SageMaker), 
            Apache Iceberg, DistDGL, Apache Spark}}
            
        \end{itemize}

%%%%%%%%%%%%%%%%%%%
\pagebreak
%%%%%%%%%%%%%%%%%%%
    \indent \resCompany{Domino Data Lab}
        \indent \resPosition{Staff Software Engineer}{Nov 2019 - Mar 2020}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            
            \resitem{Optimized real-time feature store's operational costs by 45\%.}
            \resitem{Designed consumer facing REST APIs for MLOps control plane.}
            \resitem{Designed an infrastructure-as-code template for high-volume data ingestion, enabling easy and repeatable deployments across tenant accounts.}

            \resitem{\textbf{Technologies:} \textit{Scala, Play, Python, MongoDB, AWS (Sagemaker, EMR, S3, Kinesis, Lambda, EKS)}}
            
        \end{itemize}

%%%%%%%%%%%%%%%%%%%
    \indent \resCompany{Rivigo}
        \indent \resPosition{Staff Software Engineer}{Jul 2018 - Nov 2019}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            
            \resitem{Architected a scalable data ingestion platform, enabling a centralized Data Lake to streamlined analytics and ML workflows.}
            
            \resitem{Developed cost effective serverless feature store, that accelerated ML model training and inference by standardizing features across teams.}
            
            \resitem{Reduced AWS infrastructure costs by \textbf{40\%} through optimization of service flows, transitioning from real-time to batch processing, and implementing efficient DB schemas and access patterns.}
            
            \resitem{Engineered a predictive maintenance system for truck fleet management, using sensor data feeds, enabling tracking and proactive vehicle maintenance to reduce downtime.}
            
            \resitem{Designed a flexible mapping framework supporting multiple vendors (Google Maps, Bing Maps, Map My India), optimizing route calculations and reducing operational costs by \textbf{30\%}.}
            
            \resitem{Led the transformation of a monolithic Commerce service into specialized microservices (Order, Payments, Wallet, Incentives, Fuel, Fastag, Billing).}
            
            \resitem{Implemented real-time payout system with automated retries and intelligent bank selection, alongside a comprehensive wallet system integrated with bank accounts, fuel vouchers, and Fastag top-ups.}
            
            \resitem{Developed a easy to customise, DSL-powered incentive engine enabling business analysts to define and trigger real-time coupon distribution, enhancing user engagement and operational efficiency.}

            \resitem{\textbf{Technologies:} \textit{Java, Scala, Python, Go, AWS (RDS, EMR, Glue, S3, ECS, Lambda, SNS, SQS), MongoDb, Postgres}}
            
        \end{itemize}
        
%%%%%%%%%%%%%%%%%%%

    \indent \resCompany{Adobe}
        \indent \resPosition{Computer Scientist 2}{Jul 2013 - Jul 2018}
        \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            
            \resitem{Led development of ML-based document digitization pipeline for Adobe Sense-AI cloud offerings, successfully implementing feature extraction and HTML transformation frameworks that enhanced document accessibility on mobile devices, culminating in an \textbf{US patent (US20190163733A1)} for conversion quality evaluation.}
            
            \resitem{Engineered critical performance optimizations in AEM Forms, implementing selective HTML loading and enhanced XFA PDF rendering engines, while developing comprehensive form control systems for both frontend and backend data manipulation.}
            
            \resitem{Developed multiple PDF and XFA-Form authoring and management features for the Adobe Document Cloud.}
            
            \resitem{\textbf{Technologies:} \textit{AEM, XFA PDF, Adobe Sense-AI, Scala, Java, Python, C++, Apache Spark, RNN}}
            
        \end{itemize}


%%%%%%%%%%%%%%%%%%%

    \indent \resheading{Patent}
    \begin{itemize}[leftmargin=30pt, rightmargin=-16pt]
        \resitem {\href{https://patents.google.com/patent/US10621279}{{Conversion quality evaluation for digitized forms.}}, US10621279B2, filed under Adobe.}
    \end{itemize}

%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%

    \indent \resheading{Education}
    \indent \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
        \textbf{\large Indian Institute of Technology, Guwahati} & \textit{2013} \\
        \textit{Computer Science and Engineering} & \textit{CGPA: \textbf{8.92}}
    \end{tabular*}
    \begin{itemize}[leftmargin=30pt, rightmargin=-16pt, itemsep=-2pt]
            \setlength{\itemsep}{-3pt}
            \resitem{\textbf{Project:} Parallel GPU-Accelerated Visibility Graph Construction and Shortest Path Computation for Polygonal Obstacles}
            \resitem{\textbf{Technologies:} \textit{C++, Boost, CGAL, GPGPU, CUDA, OpenCL}}
.   \end{itemize}

%%%%%%%%%%%%%%%%%%%

\end{document}
