%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}
    \newfontfamily\libertinesystemfont{Linux Libertine O}
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Saswata}{Dutta}{saswat.dutta@gmail.com | 8178349520 | Bengaluru | linkedin.com/in/saswata-dutta}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Domino Data Lab}\descript{| Technical Lead}\hfill \location{Bengaluru | Nov 2019 – Present}
\begin{tightemize}
	\item Working on Common Services, Frameworks and Enterprise team.
	(
        {\libertinesystemfont {\textbf Scala, Play, Python}}
    )
	\item Implemented public REST apis for model monitor.
	\item Refactoring and upgrading persistence layers to support latest MongoDb.
\end{tightemize}
\sectionsep

\runsubsection{Rivigo Services Pvt. Ltd.}\descript{| Principal Engineer}\hfill \location{Gurugram | Jun 2018 – Nov 2019}
\begin{tightemize}
	\item Created platform for ingesting/querying relevant data in/out of our Data Lake. Added a Feature Store to version and share data for ML models.\newline
    (
        {\libertinesystemfont {\textbf Scala, Spark, Airflow, Python, Pandas, PySpark, AWS : EMR, Lambda, S3, Glue, Athena}}
    )
	\item Refactored “Payments/Commerce” services into separate micro-services corresponding to Payments (pay-in, pay-out), Wallet, Incentives, Fuel, and Fastag.\newline
    (
        {\libertinesystemfont {\textbf Java, Scala, Spring Boot, Hibernate, MySql}}
    )
	\item Implemented realtime pay-out to suppliers via IMPS/NEFT from company accounts in ICICI, Yes bank and Axis Bank. Automated retries and refunds. Bank and payment mode selection based on the transaction details and recent success rate of the bank. Float maintenance within the company accounts.
	\item Wallet for demand and supply users which reflected the payments and incentives in realtime. This was linked with other services like bank accounts, Fuel vouchers and Fastag topups.
	\item Integration with all major vendors : IOCL, HPCL, Reliance, BPCL, to generate fuel vouchers.
	\item Rule based Incentive engine to distribute coupons to users in realtime. Rules for eligibility, and triggering of benefits were embedded in the coupon DSL which could be input by business analysts.
	\item KYC service by performing penny drop on beneficiary account to verify name and account details.
	\item Implemented framework for integration and stress testing of entire payment/commerce ecosystem.
	\item Implemented queryable application log repository in AWS Glue/Athena, for ELK cost savings.
\end{tightemize}
\sectionsep

\runsubsection{Adobe India Pvt. Ltd.}\descript{| Computer Scientist}\hfill \location{Noida/Bengaluru | 2013 – 2018}
\begin{tightemize}
	\item Feature development and performance optimisation in multiple releases of AEM Forms.\newline
    (
        {\libertinesystemfont {\textbf Scala, C++, Java, JavaScript, Python, Apache Sling/OSGI}}
    )
	\item Automatic Paper Form Capture: Lead project from inception. Created pipelines for gathering datasets, defined protocol for communication between different knowledge sources, heuristically extract structure and semantics from “ﬂat documents”, created framework for measuring KPIs, implemented the merge and presentations engine which generated the final “Adaptive Form”.
	\item HTML5 and Adaptive forms: Optimised browser footprint to allow large forms to be efficiently loaded. Built a framework for auto importing xfa-pdf controls as html widgets. Worked on layout and formatting of elements in both html and pdf rendition. Worked on backend management, formatting and validation of user data, and generation of xml/json output for persistent storage.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\runsubsection{IIT Guwahati}\descript{| M.Tech. Computer Science and Engineering}\hfill \location{Guwahati | 2011 - 2013}\\
GPA: 8.92\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\raggedright

\runsubsection{\large{Spark-Seed}}
\descript{| Scala, Apache Spark}\hfill \location{github.com/saswata-dutta/spark-seed}\\
Spark based framework to ingest data from any source, and flush to any sink. Motivation was to allow easy configuration of simple ingestion and ETL with just configuration files.\\
\sectionsep
  

\runsubsection{\large{feature-store}}
\descript{| Python, PySpark, Pandas}\hfill \location{github.com/saswata-dutta/feature-store}\\
A simple Feature-Store which allows schema evolution. Uses S3 for storage, Glue for data catalog, and Athena as SQL engine. Motivation was the lack of cost effective tooling for small to medium scale data processing.\\
\sectionsep
  

\runsubsection{\large{Eval-Expression}}
\descript{| Scala, JavaScript}\hfill \location{github.com/saswata-dutta/eval-exp}\\
A generic expression parser and evaluator with support for variables and allowing extensions to operations. Input DSL can be json or lisp.\\
\sectionsep
% \ 
\end{document}